% !TeX program = xelatex
\documentclass[
fontsize=12pt,
paper=letter,
parskip=half,
enlargefirstpage=on,    % More space on first page
fromalign=right,        % PLacement of name in letter head
fromphone=on,           % Turn on phone number of sender
fromemail=on,
fromrule=aftername,     % Rule after sender name in letter head
addrfield=off,           % Adress field for envelope with window
backaddress=off,         % Sender address in this window
subject=beforeopening,  % Placement of subject
locfield=narrow,        % Additional field for sender
foldmarks=off,           % Print foldmarks
]{scrlttr2}

\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage[canadian]{babel}
\usepackage{fontspec} % Allows font customization
\usepackage{marvosym} % Allows the use of symbol
\usepackage{csquotes}

\defaultfontfeatures{Mapping=tex-text}

\renewcommand{\normalsize}{\fontsize{11.5}{15}\selectfont}
\let\raggedsignature\raggedright

\makeatletter
\@setplength{sigbeforevskip}{\parskip}
\@setplength{refvpos}{\useplength{toaddrvpos}}
\makeatother

%\LoadLetterOption{DIN}
\setkomavar{fromname}{Alexander Schaap}
\setkomavar{fromaddress}{608-1830 Main Street West\\Hamilton, ON\\L8S 1H5}
\setkomavar{fromphone}{+1 289 775 9192}
\setkomavar{fromemail}{alexander.l.schaap@gmail.com}
\setkomavar{backaddressseparator}{\enspace\textperiodcentered\enspace}
\setkomavar{signature}{Alexander Schaap}
\setkomavar{place}{Hamilton}
\setkomavar{date}{\today}
%\setkomavar{enclseparator}{: }

\setkomavar{firsthead} {
  \centering
  {\addfontfeature{LetterSpace=20.0}\fontsize{24}{24}\selectfont\scshape \usekomavar{fromname}}\\[1mm]
  \fontsize{12}{12}\selectfont\scshape Software Engineer and Sustainability Enthusiast} 
\setkomavar{firstfoot}{
  \centering
  \addfontfeature{LetterSpace=50.0}\scshape
  {
    \renewcommand{\\}{\ {\large\textperiodcentered}\ }
    \usekomavar{fromaddress}
  }\\
  {\quad \Large\Letter} \usekomavar{fromemail} \ {\Large\Telefon} \usekomavar{fromphone}}
\begin{document}
% If you want headings on subsequent pages,
% remove the ``%'' on the next line:
% \pagestyle{headings}

\begin{letter}{Academic Sustainability Programs Office}

\setkomavar{subject}{Course Developer - Sustain 2IS3 - Intersectionality \& Sustainable Development}

\opening{Dear~Hiring~Manager,}

I am passionate about sustainability.
For 6+ years, I have collected e-waste and produced working PCs for friends and family.
I voluntarily collaborated on the Fall 2019 3S03 ``From Trash to Treasure'' course project with great satisfaction, which I hope to replicate during my current collaboration on the Repair Caf\'{e} course project.
I enjoy these opportunities to use my knowledge and experience to make a positive, measurable difference in our handling of the environment in terms of waste reduction.
In my brief role at UTS, I attempted to push for an e-waste reuse program, but due to the COVID-19 pandemic, this effort was put on hold.
Nevertheless, I believe this experience would aid in the development of new courses.
My PhD at McMaster (all but degree) demonstrates I am also a strong independent worker who can focus on a single topic for extended periods of time.
Proven industry experience has made me an effective communicator.
As an open source enthusiast, I try to give back to the community however I may.

My experience with the Academic Sustainability Programs Office have been nothing but positive, and I would be honoured to work alongside professional and driven colleagues in such a meaningful position.
I am delighted at the opportunity to give back to McMaster and the broader community for the betterment of the world as a whole.

I am confident that my expertise and passion will prove to be an asset to the Academic Sustainability Programs Office.
Thank you for your time and consideration.
I look forward to hearing from you and further discussing my qualifications.
\closing{Sincerely,}

%enclosure listing
%\encl{}

\end{letter}
\end{document}
