% !TeX program = xelatex
\documentclass[
fontsize=12pt,
paper=letter,
parskip=half,
enlargefirstpage=on,    % More space on first page
fromalign=right,        % PLacement of name in letter head
fromphone=on,           % Turn on phone number of sender
fromemail=on,
fromrule=aftername,     % Rule after sender name in letter head
addrfield=off,           % Adress field for envelope with window
backaddress=off,         % Sender address in this window
subject=beforeopening,  % Placement of subject
locfield=narrow,        % Additional field for sender
foldmarks=off,           % Print foldmarks
]{scrlttr2}

\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage[canadian]{babel}
\usepackage{fontspec} % Allows font customization
\usepackage{marvosym} % Allows the use of symbol
\usepackage{csquotes}

\defaultfontfeatures{Mapping=tex-text}

\renewcommand{\normalsize}{\fontsize{11.5}{15}\selectfont}
\let\raggedsignature\raggedright

\makeatletter
\@setplength{sigbeforevskip}{\parskip}
\@setplength{refvpos}{\useplength{toaddrvpos}}
\makeatother

%\LoadLetterOption{DIN}
\setkomavar{fromname}{Alexander Schaap}
\setkomavar{fromaddress}{608-1830 Main Street West\\Hamilton, ON\\L8S 1H5}
\setkomavar{fromphone}{+1 289 775 9192}
\setkomavar{fromemail}{alexander.l.schaap@gmail.com}
\setkomavar{backaddressseparator}{\enspace\textperiodcentered\enspace}
\setkomavar{signature}{Alexander Schaap}
\setkomavar{place}{Hamilton}
\setkomavar{date}{\today}
%\setkomavar{enclseparator}{: }

\setkomavar{firsthead} {
  \centering
  {\addfontfeature{LetterSpace=20.0}\fontsize{24}{24}\selectfont\scshape \usekomavar{fromname}}\\[1mm]
  \fontsize{12}{12}\selectfont\scshape Technical Solutions Engineer } 
\setkomavar{firstfoot}{
  \centering
  \addfontfeature{LetterSpace=50.0}\scshape
  {
    \renewcommand{\\}{\ {\large\textperiodcentered}\ }
    \usekomavar{fromaddress}
  }\\
  {\quad \Large\Letter} \usekomavar{fromemail} \ {\Large\Telefon} \usekomavar{fromphone}}
\begin{document}
% If you want headings on subsequent pages,
% remove the ``%'' on the next line:
% \pagestyle{headings}

\begin{letter}{Hiring Manager\\Google}

\setkomavar{subject}{}

\opening{Dear~Hiring~Manager,}

In response to your Technical Solutions Engineer job posting on McMaster University's OSCARplus, I have attached my resume for your review.
My experience in various roles as a liaison between available technology and people in need of solutions allows me to efficiently address customers needs and ensure their satisfaction.
Proven industry experience as a researcher/consultant has made me an effective communicator, and I genuinely enjoy helping people solve problems.

Having successfully performed troubleshooting on computers since elementary school, I bring the desired aptitude and mindset to the table.
In grad school, I solved other graduate students' Windows, Linux and network connectivity problems, and due to my versatile knowledge I quickly became the go-to person for such questions. The issues ranged from a Thunderbolt display flooding the building's wired network with packets to troubleshooting malfunctioning PC hardware.
In my Research Assistant position during this time, I researched solutions to issues raised by our industry partner, learning new systems and standards for every project.
I effectively communicated my findings via quarterly reports, presentations to upper management and weekly meetings with domain experts.
At home I enjoy working on personal projects including a more secure router using OPNsense and a server, where I use a top-level domain via dynamic DNS to access my self-hosted services.

Google has distinguished itself as a company that values intellect and creative solutions, in addition to listening to employees regarding project Maven for example.
The opposition to censorship and respect for privacy by withholding project Dragonfly are admirable and align with my personal values.
I also believe that Alphabet's extensive range of products and services via its many subsidiaries is an intelligent approach to ever-changing markets, and one that keeps customers engaged.

I am confident that my expertise and passion will prove to be an asset to the organization.
Thank you for your time and consideration.
I look forward to hearing from you and further discussing my qualifications.
\closing{Sincerely,}

%enclosure listing
%\encl{}

\end{letter}
\end{document}
