% !TeX program = xelatex
\documentclass[
fontsize=12pt,
paper=letter,
parskip=half,
enlargefirstpage=on,    % More space on first page
fromalign=right,        % PLacement of name in letter head
fromphone=on,           % Turn on phone number of sender
fromemail=on,
fromrule=aftername,     % Rule after sender name in letter head
addrfield=off,           % Adress field for envelope with window
backaddress=off,         % Sender address in this window
subject=beforeopening,  % Placement of subject
locfield=narrow,        % Additional field for sender
foldmarks=off,           % Print foldmarks
]{scrlttr2}

\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage[canadian]{babel}
\usepackage{fontspec} % Allows font customization
\usepackage{marvosym} % Allows the use of symbol
\usepackage{csquotes}

\defaultfontfeatures{Mapping=tex-text}

\renewcommand{\normalsize}{\fontsize{11.5}{15}\selectfont}
\let\raggedsignature\raggedright

\makeatletter
\@setplength{sigbeforevskip}{\parskip}
\@setplength{refvpos}{\useplength{toaddrvpos}}
\makeatother

%\LoadLetterOption{DIN}
\setkomavar{fromname}{Alexander Schaap}
\setkomavar{fromaddress}{608-1830 Main Street West\\Hamilton, ON\\L8S 1H5}
\setkomavar{fromphone}{+1 289 775 9192}
\setkomavar{fromemail}{alexander.l.schaap@gmail.com}
\setkomavar{backaddressseparator}{\enspace\textperiodcentered\enspace}
\setkomavar{signature}{Alexander Schaap}
\setkomavar{place}{Hamilton}
\setkomavar{date}{\today}
%\setkomavar{enclseparator}{: }

\setkomavar{firsthead} {
  \centering
  {\addfontfeature{LetterSpace=20.0}\fontsize{24}{24}\selectfont\scshape \usekomavar{fromname}}\\[1mm]
  \fontsize{12}{12}\selectfont\scshape Cloud Technical Residency } 
\setkomavar{firstfoot}{
  \centering
  \addfontfeature{LetterSpace=50.0}\scshape
  {
    \renewcommand{\\}{\ {\large\textperiodcentered}\ }
    \usekomavar{fromaddress}
  }\\
  {\quad \Large\Letter} \usekomavar{fromemail} \ {\Large\Telefon} \usekomavar{fromphone}}
\begin{document}
% If you want headings on subsequent pages,
% remove the ``%'' on the next line:
% \pagestyle{headings}

\begin{letter}{Hiring Manager\\Google}

\setkomavar{subject}{}

\opening{Dear~Hiring~Manager,}

In response to your Cloud Technical Residency job posting on McMaster University's OSCARplus, I have attached my resume for your review.
My education and personal interests align with the desired qualifications.
Proven industry experience as a collaborating researcher has made me an effective communicator, and I genuinely enjoy helping people solve problems.

It is my belief that I possess the right blend of software engineering and communicative skills for the position.
Throughout my undergraduate program I predominantly used Java, but learned Haskell via an elective.
I had multiple courses on database design and SQL query construction, and did well enough to subsequently be a teaching assistant for one such course.
While I have used Scala in my graduate-level programming languages class, my functional programming experience centres around Haskell and OCaml, mainly focusing on the latter for the last five years.
As an open source enthusiast, I have used Linux daily ever since I started in high school, starting with Ubuntu before moving on to Debian, Arch and Gentoo.
While I have considered the counterpart to the cloud as well by hosting some services at home, I'm looking for opportunities to learn more about the cloud.
I have been using my critical thinking and problem-solving skills for troubleshooting computers successfully and cost-effectively since elementary school.
In graduate school, I solved other graduate students' Windows, Linux and network connectivity problems, and due to my versatile knowledge I quickly became the go-to person for such questions.

Google has distinguished itself as a company that values intellect and creative solutions, in addition to listening to employees regarding project Maven and project Dragonfly for example.
Maintaining organizational flexibility and working on products and services that can make peoples' lives better appeals to me.
I also believe that Alphabet's extensive range of products and services via its many subsidiaries is an intelligent approach to ever-changing markets, and one that keeps customers engaged.

I am confident that my expertise and passion will prove to be an asset to the organization.
Thank you for your time and consideration.
I look forward to hearing from you and further discussing my qualifications.
\closing{Sincerely,}

%enclosure listing
%\encl{}

\end{letter}
\end{document}
