% !TeX program = xelatex
\documentclass[
fontsize=12pt,
paper=letter,
parskip=half,
enlargefirstpage=on,    % More space on first page
fromalign=right,        % PLacement of name in letter head
fromphone=on,           % Turn on phone number of sender
fromemail=on,
fromrule=aftername,     % Rule after sender name in letter head
addrfield=off,           % Adress field for envelope with window
backaddress=off,         % Sender address in this window
subject=beforeopening,  % Placement of subject
locfield=narrow,        % Additional field for sender
foldmarks=off,           % Print foldmarks
]{scrlttr2}

\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage[canadian]{babel}
\usepackage{fontspec} % Allows font customization
\usepackage{marvosym} % Allows the use of symbol
\usepackage{csquotes}

\defaultfontfeatures{Mapping=tex-text}

\renewcommand{\normalsize}{\fontsize{11.5}{15}\selectfont}
\let\raggedsignature\raggedright

\makeatletter
\@setplength{sigbeforevskip}{\parskip}
\@setplength{refvpos}{\useplength{toaddrvpos}}
\makeatother

%\LoadLetterOption{DIN}
\setkomavar{fromname}{Alexander Schaap}
\setkomavar{fromaddress}{608-1830 Main Street West\\Hamilton, ON\\L8S 1H5}
\setkomavar{fromphone}{+1 289 775 9192}
\setkomavar{fromemail}{alexander.l.schaap@gmail.com}
\setkomavar{backaddressseparator}{\enspace\textperiodcentered\enspace}
\setkomavar{signature}{Alexander Schaap}
\setkomavar{place}{Hamilton}
\setkomavar{date}{\today}
%\setkomavar{enclseparator}{: }

\setkomavar{firsthead} {
  \centering
  {\addfontfeature{LetterSpace=20.0}\fontsize{24}{24}\selectfont\scshape \usekomavar{fromname}}\\[1mm]
  \fontsize{12}{12}\selectfont\scshape Software Engineer } 
\setkomavar{firstfoot}{
  \centering
  \addfontfeature{LetterSpace=50.0}\scshape
  {
    \renewcommand{\\}{\ {\large\textperiodcentered}\ }
    \usekomavar{fromaddress}
  }\\
  {\quad \Large\Letter} \usekomavar{fromemail} \ {\Large\Telefon} \usekomavar{fromphone}}
\begin{document}
% If you want headings on subsequent pages,
% remove the ``%'' on the next line:
% \pagestyle{headings}

\begin{letter}{Hiring Manager\\Google}

\setkomavar{subject}{}

\opening{Dear~Hiring~Manager,}

In response to your Software Engineer job posting on McMaster University's OSCARplus, I have attached my resume for your review.
My PhD research on typed code generation allows me to contribute in novel ways to software, particularly where program families and modularization are significant.
Proven industry experience as a collaborating researcher has made me an effective communicator.

It is my belief that my research can be applied to benefit existing and new software projects.
My research consists of creating program family generators, whose output approximates hand-written code minus much of the function-call overhead.
While variabilities in software product lines typically consist of low-level design choices such as sorting algorithms or data structures, design choices such as programming paradigm and module decomposition have the potential to be variabilities too.
Using a typed metaprogramming approach ensures that the output is both syntactically and semantically correct.
Throughout my undergraduate program I predominantly used Java.
I took courses on database design and SQL query construction, and did well enough to subsequently be a teaching assistant for the latter.
Additionally, I took both the undergraduate-level and graduate-level algorithms and data structures course, and much of the Research Assistant work focused in some way on software design and good practices.
As an open source enthusiast, I have used Linux daily ever since I started in high school.
In my free time I have dabbled with Javascript in the context of the Angular framework.

Google has distinguished itself as a company that values intellect and creative solutions, in addition to listening to employees regarding project Maven and project Dragonfly for example.
Maintaining organizational flexibility and working on products and services that can make peoples' lives better both appeal to me.
I also believe that Alphabet's extensive range of products and services via its many subsidiaries is an intelligent approach to ever-changing markets, and one that keeps customers engaged.

I am confident that my expertise and passion will prove to be an asset to the organization.
Thank you for your time and consideration.
I look forward to hearing from you and further discussing my qualifications.
\closing{Sincerely,}

%enclosure listing
%\encl{}

\end{letter}
\end{document}
