% !TeX program = xelatex
\documentclass[
fontsize=12pt,
paper=letter,
parskip=half,
enlargefirstpage=on,    % More space on first page
fromalign=right,        % PLacement of name in letter head
fromphone=on,           % Turn on phone number of sender
fromemail=on,
fromrule=aftername,     % Rule after sender name in letter head
addrfield=off,           % Adress field for envelope with window
backaddress=off,         % Sender address in this window
subject=beforeopening,  % Placement of subject
locfield=narrow,        % Additional field for sender
foldmarks=off,           % Print foldmarks
]{scrlttr2}

\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage[canadian]{babel}
\usepackage{fontspec} % Allows font customization
\usepackage{marvosym} % Allows the use of symbol
\usepackage{csquotes}

\defaultfontfeatures{Mapping=tex-text}

\renewcommand{\normalsize}{\fontsize{11.5}{15}\selectfont}
\let\raggedsignature\raggedright

\makeatletter
\@setplength{sigbeforevskip}{\parskip}
\@setplength{refvpos}{\useplength{toaddrvpos}}
\makeatother

%\LoadLetterOption{DIN}
\setkomavar{fromname}{Alexander L. Schaap}
\setkomavar{fromaddress}{608-1830 Main Street West\\Hamilton, ON\\L8S 1H5}
\setkomavar{fromphone}{+1 289 775 9192}
\setkomavar{fromemail}{alexander.l.schaap@gmail.com}
\setkomavar{backaddressseparator}{\enspace\textperiodcentered\enspace}
\setkomavar{signature}{Alexander Schaap}
\setkomavar{place}{Hamilton}
\setkomavar{date}{\today}
%\setkomavar{enclseparator}{: }

\setkomavar{firsthead} {
  \centering
  {\addfontfeature{LetterSpace=20.0}\fontsize{24}{24}\selectfont\scshape \usekomavar{fromname}}\\[1mm]
  \fontsize{12}{12}\selectfont\scshape Software Engineer and Sustainability Enthusiast} 
\setkomavar{firstfoot}{
  \centering
  \addfontfeature{LetterSpace=50.0}\scshape
  {
    \renewcommand{\\}{\ {\large\textperiodcentered}\ }
    \usekomavar{fromaddress}
  }\\
  {\quad \Large\Letter} \usekomavar{fromemail} \ {\Large\Telefon} \usekomavar{fromphone}}
\begin{document}
% If you want headings on subsequent pages,
% remove the ``%'' on the next line:
% \pagestyle{headings}

\begin{letter}{}

\setkomavar{subject}{Front-End Javascript Engineer (MoveSnap)}

\opening{Dear~James,}


My experience with RBC, starting as a child of a client, has always been excellent.
Additionally, I believe RBC's strategy of branching out into successful ventures will pay off.
I would like to help effect meaningful change to people's lives through my passion for building beautiful front-end full-stack solutions.
I believe my technical aptitude and broad range of skills to be a valuable addition to RBC Ventures.

In high school and undergrad, I created front-ends for Joomla-based websites, gaining experience creating W3C and AODA compliant user experiences in HTML, CSS and Javascript.
I resolved cross-browser compatibility and layout issues (dating back to IE 6), and optimized loading time.
I used MySQL databases in conjunction with Joomla, and taught an undergrad relational databases course; I also took grad-level algorithms and data structures course.
My graduate research focuses on abstraction through architecting and refining APIs, and using them; I relied on unit testing throughout.
I have also created a tiny API in Node.js in my free time.
My foray into {\nobreak DevOps} includes writing a continuous integration pipeline in Gitlab to configure a Docker image, compile code, and run unit tests.
As a Research Assistant, I gained seven years of research and software development experience in a collaborative automotive setting, regularly learning on the job and quickly achieving the desired results.
My GitHub activity demonstrates my proficiency in Git and my contributions to open-source projects via pull requests.

I am confident that my expertise and passion will prove to be an asset to RBC Ventures and MoveSnap.
Thank you for your time and consideration.
I look forward to hearing from you and further discussing my qualifications.
\closing{Sincerely,}

%enclosure listing
%\encl{}

\end{letter}
\end{document}