% !TeX program = xelatex
\documentclass[
fontsize=12pt,
paper=letter,
parskip=half,
enlargefirstpage=on,    % More space on first page
fromalign=right,        % PLacement of name in letter head
fromphone=on,           % Turn on phone number of sender
fromemail=on,
fromrule=aftername,     % Rule after sender name in letter head
addrfield=off,           % Adress field for envelope with window
backaddress=off,         % Sender address in this window
subject=beforeopening,  % Placement of subject
locfield=narrow,        % Additional field for sender
foldmarks=off,           % Print foldmarks
]{scrlttr2}

\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage[canadian]{babel}
\usepackage{fontspec} % Allows font customization
\usepackage{marvosym} % Allows the use of symbol
\usepackage{csquotes}

\defaultfontfeatures{Mapping=tex-text}

\renewcommand{\normalsize}{\fontsize{11.5}{15}\selectfont}
\let\raggedsignature\raggedright

\makeatletter
\@setplength{sigbeforevskip}{\parskip}
\@setplength{refvpos}{\useplength{toaddrvpos}}
\makeatother

%\LoadLetterOption{DIN}
\setkomavar{fromname}{Alexander L. Schaap}
\setkomavar{fromaddress}{608-1830 Main Street West\\Hamilton, ON\\L8S 1H5}
\setkomavar{fromphone}{+1 289 775 9192}
\setkomavar{fromemail}{alexander.l.schaap@gmail.com}
\setkomavar{backaddressseparator}{\enspace\textperiodcentered\enspace}
\setkomavar{signature}{Alexander Schaap}
\setkomavar{place}{Hamilton}
\setkomavar{date}{\today}
%\setkomavar{enclseparator}{: }

\setkomavar{firsthead} {
  \centering
  {\addfontfeature{LetterSpace=20.0}\fontsize{24}{24}\selectfont\scshape \usekomavar{fromname}}\\[1mm]
  \fontsize{12}{12}\selectfont\scshape Software Engineer and Sustainability Enthusiast} 
\setkomavar{firstfoot}{
  \centering
  \addfontfeature{LetterSpace=50.0}\scshape
  {
    \renewcommand{\\}{\ {\large\textperiodcentered}\ }
    \usekomavar{fromaddress}
  }\\
  {\quad \Large\Letter} \usekomavar{fromemail} \ {\Large\Telefon} \usekomavar{fromphone}}
\begin{document}
% If you want headings on subsequent pages,
% remove the ``%'' on the next line:
% \pagestyle{headings}

\begin{letter}{Academic Sustainability Programs Office}

\setkomavar{subject}{Software Engineer -- Irmin}

\opening{Dear~Hiring~Manager,}

I am passionate about storage systems.
From reading Scott Chacon's ``Pro Git'' book explaining how Git can be seen as a filesystem, to the Zettabyte File System (ZFS), on which I wrote a course report, taking a teaching assistant position for a databases course, taking the first steps to using MongoDB in my spare time, and researching the most efficient (yet accessible) compression scheme for comic book archives, I feel my interest would be an asset.

My PhD at McMaster demonstrates I am also a strong independent worker who can focus on a single topic for extended periods of time.
Proven industry experience has made me an effective communicator.
While I do not have any publications about my research beyond my master's thesis yet, I believe that the experience developing program generators in OCaml would be beneficial as a software engineer on the Irmin project.
I am also a proponent of open-source; I try to give back to the community however I may.
I use Gentoo Linux daily on my desktop, and Debian on my home server. While I spend most of my time on my degree, my Github activity will show you my efforts to contribute to open-source projects.

Tarides has been of interest to me for some time now.
Apart from being one of the few OCaml-centric companies, the unikernel approach also seems worthwhile, especially from a security point of view.
Since you employ many top minds from well-known universities, I also expect it to be an inspiring environment to work in.

I am confident that my expertise and passion will prove to be an asset to Tarides and the Irmin project.
Thank you for your time and consideration.
I look forward to hearing from you and further discussing my qualifications.
\closing{Sincerely,}

%enclosure listing
%\encl{}

\end{letter}
\end{document}